Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2015-08-13 writeup/gz_hubble_data.tex
added some figures of hubble debiased data

\subsection{Approach to debiasing morphological classifications}

@@

In Figure \ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the FERENGI images relative to their lowest simulated redshift ($\rm z_{sim}=0.3$). For each simulated redshift value $z$, and at fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$. Only images corresponding to galaxies which also had FERENGI images at $z=0.3$ were included in this plot, which include 4031 out of the total 6624.

@@

@@

\begin{table*}
\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
\hline
Correctable                        & 2,438   & 21,522 & 28,52 & 1,146  & 1,040   & 0       & 28,998\\
Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
No Correction Needed ($z \le 0.3$) & 698     & 9,679 & 1,012 & 171    & 199     & 37,545  & 49,034\\ 
NEI                                & 2,621   & 34,888 & 1,960 & 728    & 2,053   & 0       & 42,250\\
No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
\hline\hline
\end{tabular}
\end{table*}

>>>>

\subsection{Approach to debiasing morphological classifications}
\label{sec:zeta}

@@

In Figure \ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in Sextractor; this includes 3,959 of the total 6,466 images. For each simulated redshift value $z$, and at fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.

@@

Using this approach, 52\% of the \ferengi{} images were found to have single-valued relationships between their $p_{\rm features}$ values at high and low redshift (see Table \ref{ferengi_corrections} for a summary.) Only these images were used in determining the $\zeta$ function (Section \ref{sec:zeta}).

\begin{table}
\caption{Distribution of \ferengi{} images analysed in Figure \ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure \ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (green regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding sub-bins (purple regions).   \label{ferengi_corrections}}
\begin{tabular}{lcc}
\hline \hline
				   & N     & \% \\
\hline 
Correctable                        & 2,057   & 52\% \\
Uncorrectable                      & 1,732   & 44\% \\
NEI                                & 170     &  4\%\\
Total                              & 3,959   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{table*}
\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
\hline
Correctable                        & 2,325   & 20,669 & 2,748 & 1,074  & 1,022   & 0       & 27,838\\
Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
No Correction Needed ($z \le 0.3$) & 967     & 11,693 & 1,190 & 280    & 247     & 37,545  & 51,922\\ 
NEI                                & 2,465   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,792\\
No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
\hline\hline
\end{tabular}
\end{table*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distribution of things for 3 groups. }
\label{fig:z_mu_p}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased vs weighted values for 3 groups.}
\label{fig:features_corrections}
\end{center}
\end{figure*}
